Measurement of deeply virtual Compton scattering off Helium-4 with CLAS at Jefferson Lab

### 2020-05-11 eg6-letters/long-paper/prc-dvcshelium.tex
Update fig 17 and add line numbers for review

\documentclass[aps,prc,preprint,superscriptaddress]{revtex4}
%\usepackage{amsmath,amssymb}             % AMS Math
%\usepackage[francais]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern,textcomp}
%\usepackage[left=3.5cm,right=2.5cm,top=2cm,bottom=2cm,includefoot,includehead,headheight=15pt]{geometry}
\usepackage{setspace}
\usepackage{microtype}
\usepackage{epigraph}
\usepackage{natbib}
%\usepackage[scaled]{helvet}
%\usepackage[pagebackref,hyperindex=true]{hyperref}
%\usepackage{pdfpages}
\usepackage{graphicx}
\usepackage{array}
\usepackage{amsmath}

@@

\input author_list.tex

\date{\today}

@@

% insert suggested PACS numbers in braces on next line
\pacs{}

\maketitle

@@

\begin{figure}[tbp!]
\center
\includegraphics[width=7.4cm]{fig3/ALU_90_p_vs_Q2_tcomp.pdf}
\includegraphics[width=7.4cm]{fig3/ALU_90_p_vs_t_tcomp.pdf}
%\includegraphics[width=7cm]{fig3/ALU_90_p_vs_x_shortscenrario.pdf}
	\caption{The BSA at 90° ($A_{LU}^{Incoh} (90^\circ)$) as a
	function of $Q^2$ and $-t$, using the photon based $t$ definition (empty red)
	and the proton based $t^\prime$ definition (full black).}
	%TODO we could remove HERMES and the models on these
\label{fig:ttpComp}
\end{figure}

@@

\begin{acknowledgments}
The authors acknowledge the staff of the Accelerator and Physics Divisions at 
the Thomas Jefferson National Accelerator Facility who made this experiment 
possible. This work was supported in part by the Chilean Comisi\'on Nacional de 
Investigaci\'on Cient\'ifica y Tecnol\'ogica (CONICYT), by CONICYT PIA grant 
ACT1413, the Italian Instituto Nazionale di Fisica Nucleare, the French Centre 
National de la Recherche Scientifique, the French Commissariat \`a l'Energie 
Atomique, the U.S. Department of Energy under Contract No. DE-AC02-06CH11357, 
the United Kingdom Science and Technology Facilities Council (STFC), the 
Scottish Universities Physics Alliance (SUPA), the National Research Foundation 
of Korea, and the Office of Research and Economic Development at Mississippi 
State University. M.~Hattawy also acknowledges the support of the Consulat 
G\'en\'eral de France \`a J\'erusalem. This work has received funding from 
the European Research Council (ERC) under the European Union’s Horizon 2020 
research and innovation programme (Grant agreement No. 804480). The Southeastern Universities Research 
Association operates the Thomas Jefferson National Accelerator Facility for the 
United States Department of Energy under Contract No. DE-AC05-06OR23177.
\end{acknowledgments}

@@

The Fourier coefficients for BH contributions are defined as:
\begin{eqnarray}
c_0^{BH} = & \bigg[ & \left\{ {(2-y)}^2 + y^2{(1+\epsilon^2)}^2 \right\} 
\left\{ \frac{\epsilon^2 Q^2}{t} + 4 (1-x_A) + (4x_A+\epsilon^2) \frac{t}{Q^2} 
\right\} \nonumber \\
& \phantom{\bigg[} & + 2 \epsilon^2 \left\{ 4(1-y)(3+2\epsilon^2) + y^2(2-\epsilon^4) 
\right\} - 4 x_A^2{(2-y)}^2 (2+\epsilon^2) \frac{t}{Q^2} \nonumber \\
& \phantom{\bigg[} & + 8 K^2 \frac{\epsilon^2 Q^2}{t} \,\,\,\,\,\,\, \bigg] F_A^2(t)  \\
c_1^{BH} = & \phantom{\bigg[} & -8 (2-y) K \left\{ 2 x_A + \epsilon^2 - 
\frac{\epsilon^2 Q^2}{t} \right\} F_A^2(t)  \\
c_2^{BH} = & \phantom{\bigg[} & 8 K^2 \frac{\epsilon^2 Q^2}{t} F_A^2(t) 
\end{eqnarray} 
where $F_A(t)$ is the electromagnetic form factor of the $^4$He. 
The coefficient for the DVCS contribution is given by: 
\begin{equation}
   c_0^{DVCS}= 2 \frac{2-2y+y^2 + \frac{\epsilon^2}{2}y^2}{1 + \epsilon^2} \, 
   {\mathcal H}_A {\mathcal H}^{\star}_A 
   \label{eq:c0DVCS}
\end{equation}

@@

% Create the reference section using BibTeX:
\bibliography{hadro.bib}

>>>>

\documentclass{article}
\usepackage[left=3.5cm,right=2.5cm,top=2cm,bottom=2cm,includefoot,includehead,headheight=15pt]{geometry}
\usepackage{lineno}
%\documentclass[aps,prc,preprint,superscriptaddress]{revtex4}
%\usepackage{amsmath,amssymb}             % AMS Math
%\usepackage[francais]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern,textcomp}
\usepackage{setspace}
\usepackage{microtype}
\usepackage{epigraph}
\usepackage{natbib}
%\usepackage[scaled]{helvet}
%\usepackage[pagebackref,hyperindex=true]{hyperref}
%\usepackage{pdfpages}
\usepackage{graphicx}
\usepackage{array}
\usepackage{amsmath}

%TODO
\let\oldequation\equation
\let\oldendequation\endequation

\renewenvironment{equation}
  {\linenomathNonumbers\oldequation}
  {\oldendequation\endlinenomath}

@@

%\input author_list.tex

\date{\today}
%TODO
\maketitle
\linenumbers

@@

% insert suggested PACS numbers in braces on next line
%\pacs{}

%\maketitle

@@

\begin{figure}[tbp!]
\center
\includegraphics[width=15cm]{fig3/t_tprime_ALU_90_p_shortscenrario.pdf}
	\caption{The BSA at 90° ($A_{LU}^{Incoh} (90^\circ)$) as a
	function of $Q^2$, $x_{B}$ and $-t$, using the photon based $t$ definition (red)
	and the proton based $t^\prime$ definition (black).}
\label{fig:ttpComp}
\end{figure}

@@

%TODO
\section{Acknowledgments}
%\begin{acknowledgments}
The authors acknowledge the staff of the Accelerator and Physics Divisions at 
the Thomas Jefferson National Accelerator Facility who made this experiment 
possible. This work was supported in part by the Chilean Comisi\'on Nacional de 
Investigaci\'on Cient\'ifica y Tecnol\'ogica (CONICYT), by CONICYT PIA grant 
ACT1413, the Italian Instituto Nazionale di Fisica Nucleare, the French Centre 
National de la Recherche Scientifique, the French Commissariat \`a l'Energie 
Atomique, the U.S. Department of Energy under Contract No. DE-AC02-06CH11357, 
the United Kingdom Science and Technology Facilities Council (STFC), the 
Scottish Universities Physics Alliance (SUPA), the National Research Foundation 
of Korea, and the Office of Research and Economic Development at Mississippi 
State University. M.~Hattawy also acknowledges the support of the Consulat 
G\'en\'eral de France \`a J\'erusalem. This work has received funding from 
the European Research Council (ERC) under the European Union’s Horizon 2020 
research and innovation programme (Grant agreement No. 804480). The Southeastern Universities Research 
Association operates the Thomas Jefferson National Accelerator Facility for the 
United States Department of Energy under Contract No. DE-AC05-06OR23177.
%\end{acknowledgments}

@@

The Fourier coefficients for BH contributions are defined as:
\begin{eqnarray}
c_0^{BH} = & \bigg[ & \left\{ {(2-y)}^2 + y^2{(1+\epsilon^2)}^2 \right\} 
\left\{ \frac{\epsilon^2 Q^2}{t} + 4 (1-x_A) + (4x_A+\epsilon^2) \frac{t}{Q^2} 
\right\} \nonumber \\
& \phantom{\bigg[} & + 2 \epsilon^2 \left\{ 4(1-y)(3+2\epsilon^2) + y^2(2-\epsilon^4) 
\right\} - 4 x_A^2{(2-y)}^2 (2+\epsilon^2) \frac{t}{Q^2} \nonumber \\
pdflatex prc-dvcshelium.tex
& \phantom{\bigg[} & + 8 K^2 \frac{\epsilon^2 Q^2}{t} \,\,\,\,\,\,\, \bigg] F_A^2(t)  \\
c_1^{BH} = & \phantom{\bigg[} & -8 (2-y) K \left\{ 2 x_A + \epsilon^2 - 
\frac{\epsilon^2 Q^2}{t} \right\} F_A^2(t)  \\
c_2^{BH} = & \phantom{\bigg[} & 8 K^2 \frac{\epsilon^2 Q^2}{t} F_A^2(t) 
\end{eqnarray} 
where $F_A(t)$ is the electromagnetic form factor of the $^4$He. 
The coefficient for the DVCS contribution is given by: 
\begin{equation}
   c_0^{DVCS}= 2 \frac{2-2y+y^2 + \frac{\epsilon^2}{2}y^2}{1 + \epsilon^2} \, 
   {\mathcal H}_A {\mathcal H}^{\star}_A 
   \label{eq:c0DVCS}
\end{equation}

@@

% Create the reference section using BibTeX:
%TODO
\bibliographystyle{unsrt}
\bibliography{hadro.bib}
